Psych 254 Replication Project Analysis

### 2016-06-24 analysis.Rmd
updates

project_keys <- project_plan$project_key # Find user names that are included in analysis
# For each user_

temp_project_keys <- c("smraposo","jreynolds","jmarias","ehermann", "mkeil") # Only do users we have data for currently

# Run all respective R code - need loop because project_keys same variable name
rm("project_info") # In case var is saved
for(project_key in project_keys) { # change from temp - test; project_key <- "smraposo"
  print(paste0("Running ",project_key))
  fp <- paste0("project_analyses/",project_key,".R")
  #source(fp)
  tryCatch(source(fp), error=function(e) {print(e)}) 
  if(exists("project_info")) { # If has project_info dataframe
    all_project_info <- bind_rows(all_project_info,project_info) # add to all data
    rm("project_info") # In case other file does not same
  } else {
    errors <- c(errors,paste0(project_key," is missing project_info"))
  }
}

```

>>>>

project_keys <- project_plan$project_key # Find user names that are included in

passing <- c("mkeil","jreynolds","jmarias","jsalloum","ehermann",
             "jedtan", "lampinen", "salehi")
failing <- c("sraposo", "auc", "rhiac")

# Run all respective R code - need loop because project_keys same variable name
for(project_key in passing) { # project_keys
  fp <- paste0("project_analyses/",project_key,".R")

  print(fp)

  tryCatch(source(fp), 
           error = function(e) {
             errors <- c(errors, paste0(project_key," has an error in .R file"))
             }
           )

  # If has project_info dataframe, add to all data
  if(exists("project_info")) { 
    all_project_info <- bind_rows(all_project_info,project_info) 
    # rm("project_info") # In case other file does not same
  } else {
    errors <- c(errors,paste0(project_key," is missing project_info"))
  }
}
```
